Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-13 draft.tex
improvements to the equations and descriptions for the extracted features

					is calculated as follows:
					\[ 20log\frac{\gamma_{i}}{\iota_{i}} \]

@@

					\[p_{i} = s(max(H_{i}))\]
					Then, given an offset \(x\), the pitch fluctuations can be calculated as
					follows:
					\[p_{i}-p_{i-x}\]

@@

					frequency cycles in comparison to the nearest x neighbors using the following
					method:
					\[ \frac{ \frac{1}{N-1}\sum_{i=1}^{N-1}|T_{i}

@@

					{\frac{1}{N}\sum_{i=1}^{N}T_{i}} \]
					where \(T_{i}\) represents the extracted fundamental frequency lengths and
					\(N\) is the number of fundamental frequency periods.

@@

					not a guarantee of a synthetic voice.

@@

					\[ \frac{ \frac{1}{N-1}\sum_{i=1}^{N-1}|A_{i}

@@

					{\frac{1}{N}\sum_{i=1}^{N}A_{i}} \]

@@

			The features we consider imperceptible are described as follow:

>>>>

					\(hnr_{i}\) is calculated as follows:
					\[ hnr_{i} = 20log\frac{\gamma_{i}}{\iota_{i}}. \]

@@

					\[p_{i} = s(max(H_{i})).\]
					Then, given an offset \(x\), the pitch fluctuation at cycle \(i\), \(pf_{i}\),
					can be calculated as follows:
					\[pf_{i} = p_{i}-p_{i-x}.\]

@@

					frequency cycles in comparison to the nearest x neighbors. The jitter of a
					sample in relation to the nearest \(x\) samples can be described as follows:
					\[ jitter(x) = \frac{ \frac{1}{N-1}\sum_{i=1}^{N-1}|T_{i}

@@

					{\frac{1}{N}\sum_{i=1}^{N}T_{i}}, \]
					where \(T_{i}\) represents the extracted fundamental frequency length at cycle
					\(i\), \(N\) is the number of fundamental frequency periods and \(m\) is
					\(\lfloor \frac{x}{2} \rfloor\)

@@

					not a guarantee of a synthetic voice. The shimmer of a sample in comparison to
					the nearest \(x\) fundamental frequency cycles is calculated as follows:

@@

					\[ shimmer(x) = \frac{ \frac{1}{N-1}\sum_{i=1}^{N-1}|A_{i}

@@

					{\frac{1}{N}\sum_{i=1}^{N}A_{i}}, \]
					where \(A_{i}\) is the amplitude at cycle \(i\), \(N\) is the number of
					fundamental frequency cycles in the sample and \(m\) is once again 
					\(\lfloor \frac{x}{2} \rfloor\)

@@

			The features we consider imperceptible are described as follows:
